\documentclass{article}

\usepackage[letterpaper, top=3cm, bottom=3cm, right=2.5cm, left=2.5cm]{geometry}
\usepackage[neverdecrease]{paralist}

\setdefaultleftmargin{1in}{0.5in}{}{}{}{}

\begin{document}

\begin{center}
\Huge{CONSTITUTION}
% We, the animals of [adjective][species], in order to form a more purrfect union...
\end{center}

\bigskip

\large{\underline{ARTICLE I --- NAME}}

\emph{Section 1. Title}: ``[adjective][species]'' \emph{or} ``[a][s]''.

\emph{Section 2. Tagline}: ``The Furry World from the Inside Out''.

\emph{Section 3. Business Name}: ``[adjective][species], Ltd''.

\bigskip

\large{\underline{ARTICLE II --- PURPOSE}}

\emph{Section 1. Goals of the Organization}: [adjective][species] aims to provide a grounds for the exploration of the furry subculture through:
\begin{enumerate}
  \item non-fiction writing on the topic of the furry subculture,
  \item The Furry Survey and the presentation of its results,
  \item interaction with the furry subculture through convention panels, informative guides, other informative or promotional materials, and
  \item interaction with the non-furry world at large through the above means.
\end{enumerate}

\bigskip

\large{\underline{ARTICLE III --- MEMBERSHIP}}

\emph{Section 1. Active Members}: All active members may vote or hold office.  Active membership is open to:
\begin{itemize}
  \item all authors that have contributed or pledged to contribute three articles or more to the [adjective][species] website, as well as
  \item any additional individuals who have requested membership and been voted in by existing members via email by a simple majority (half plus one).
\end{itemize}

\emph{Section 2. Membership Rules of Order}: All members are encouraged to participate in business meetings as well as in comments on the [adjective][species] website, any [a][s] panels, and ancillary services such as the [a][s] Slack network, the [a][s] Twitter, and the [a][s] Trello boards.  Members are also required to keep an open mind to the works of others, giving constructive criticism where applicable and praise where it is due.

[adjective][species] and its members are governed by this constitution and by the [adjective][species] Code of Conduct solely within the context of [a][s].

\emph{Section 3. Duties of Members}: Members are required to do their best to attend business meetings, during which officers are elected and bylaws and amendments are voted on.  No stipulations are placed on members regarding the production of content for [adjective][species] in any way.

\emph{Section 4. Disciplinary actions on Members}: A member may be disciplined by the officers of the organization if:
\begin{enumerate}
  \item they blatantly disregard the rules set forth in the constitution, and
  \item continue to do so after being approached by any member, after which
  \item a written notice of disciplinary action stipulating 7 days as the offending member's period of appeal, which gives the offending member
  \begin{itemize}
    \item the opportunity to speak on their own behalf and
    \item the right to appeal the disciplinary action by means of a hearing consisting of an officer, any members wishing to take part, and any victims or witnesses of/to the offense.
  \end{itemize}
\end{enumerate}

Disciplinary action will take the form of:
\begin{enumerate}
  \item a temporary suspension of the ability to produce content for the [adjective][species] website lasting at least one month and no more than six months,
  \item a temporary or permanent suspension of the ability to interact with ancillary services pertaining to [a][s] such as the Slack and the Twitter account, and
  \item a probationary period lasting six months during which any violation of the rules of order or the code of conduct will result in removal.
\end{enumerate}

\emph{Section 5. Removal of Members}: A member may be removed from the organization if:
\begin{itemize}
  \item they are disciplined as mentioned above three times within three years, or
  \item they violate the conditions of their disciplinary actions.
\end{itemize}

A member who has been removed will have content attributed to them sequestered from the [adjective][species] website and have their name removed from the list of members.  Removal may be reversed and membership reinstated by a two-thirds vote of active membership.

\emph{Section 8. Conflicts of Interest}: During disciplinary action, in the case of a conflict of interest, the interested party may speak for the accused party leading up to the appeals deadline, but may not vote during the appeals process.  A conflict of interest may be defined by either of the interested parties, or a vote and a second from the members of the organization.

\emph{Section 7. Withdrawal of Members}: A member may withdraw from the organization of their own will at any time, and request that their works be sequestered and their name removed from the list of members.  Members who withdrew on their own will may be reinstated at their request.

\bigskip

\large{\underline{ARTICLE IV --- OFFICERS}}

\emph{Section 1. Special Officers}: President -- Madison Scott-Clary (Makyo)

\emph{Section 2. Elected Officers}: Editor (general) -- Matt Healey (JM)

\emph{Section 3. Duties of Officers}: It shall be the duties of the president to organize meetings, to call ahead to locations that require such for meetings that occur in person, and to maintain correspondence between the members of the organization and any outside entities that the organization is affiliated with at any point during its existence.

It shall be the duties of the president to manage finances, to adhere to any rules set forth in article VIII below, and to disburse money via the [adjective][species] account to any entity as needed and decided upon by the organization.

It shall be the duties of the editors to source and schedule content for the [adjective][species] site within the area of their expertise, and to interact with authors to ensure that they have a positive experience working with [a][s].

It shall be the duty of all officers to maintain the [adjective][species] Trello board for transparency within and outside the organization.

\emph{Section 4. Election of Officers}: Officers are elected in the following way:
\begin{enumerate}
  \item a member may volunteer or be nominated for an officer position, followed by
  \item a second on on the nomination from another member, whereupon
  \item the group will vote by email, where
  \item a simple majority (half plus one) will decide the vote.
\end{enumerate}

\emph{Section 5. Removal of Officers}: An elected officer may be demoted within the organization to the level of member and disciplined as in \S III-5 if:
\begin{enumerate}
  \item they blatantly disregard the rules set forth in the constitution or blatantly neglects their duties to the detriment of the organization, and
  \item continue to do so after being approached by any member, after which
  \item a written notice of removal stipulating 7 days as the offending officer's remaining time span in the organization, which gives the offending member
  \begin{itemize}
    \item the opportunity to speak on their own behalf and
    \item the right to appeal the removal by means of a hearing consisting of the entire organization.
  \end{itemize}
\end{enumerate}

\emph{Section 6. Withdrawal of Officers}: An officer may withdraw their position as an officer and become a member or withdraw from the organization completely of their own free will at any time.

\emph{Section 7. Removal or Withdrawal of Special Officers}: Special officers hold assets related to the organization including but not limited to servers, domain names, admin rights, and contacts.  The removal or withdrawal process remains the same for elected officers, except that the disposition of the assets that they control will be decided upon the time of the officer's removal.

\bigskip

\large{\underline{ARTICLE V --- MEETINGS}}

\emph{Section 1. Business Meetings}: Business meetings may be called at a time determined by an officer at least three days in advance so that the majority of members can attend with the requirement that at least one officer can be present.

\emph{Section 2. Executive Board Meetings}: Executive board meetings shall not be held except in emergency situations.

\bigskip

\large{\underline{ARTICLE VI --- AMENDMENTS}}

\emph{Section 1. Filing Amendments}: This constitution may be amended at any regular business meeting of the organization by two-thirds vote of active membership, provided that the amendment has been submitted to the membership in writing at least one week prior to the business meeting.

\bigskip

\large{\underline{ARTICLE VII --- FINANCIAL STRUCTURE}}

\emph{Section 1. Duties of the President}: It shall be the duty of the president to keep track of record keeping and required signatures for any transactions, as well as ensuring compliance with Colorado state law on appropriate use of funds.

\emph{Section 2. List of Assets with Financial Impact}: A list of assets with financial impact will be kept on file with the constitution.

\bigskip

\large{\underline{ARTICLE VIII --- BYLAWS}}

\emph{Section 1. Method of Amending Bylaws}: Bylaws may be amended through a simple majority by way of an email vote provided that the amendment is brought before the members in writing and explained clearly by the member bringing the amendment before the organization.

\newpage

I, Madison Scott-Clary, as president of this organization and with the approval of the members and officers, sign my approval of this constitution digitally and date its acceptance on \emph{March 26, 2016}.

Signatures may be viewed at https://github.com/adjspecies/governance, along with resources mentioned in this constitution.

\bigskip

\newpage

\begin{center}
\Huge{AMENDMENTS}
\end{center}

\end{document}
